Social Feedback For Robotic Collaboration

### 2016-05-22 paper.tex
comments

\begin{abstract}
Robotic collaboration requires not just communication from the human to the robot, but also from the robot to the human. We call this robot-to-human communication \emph{social feedback}. In order to flexibly and intelligently generate social feedback, we describe a partially Observable Markov Decision Process that incorporates the human's belief about the robot's intent. Doing so incentivizes the robot to communicate its current state in order to allow the human participant to make informed decisions about their next actions. Initial evaluation in simulation shows improvement in interaction length in a toy domain while maintaining near-perfect accuracy. 
\end{abstract}

@@

Markov Decision Processes (MDPs) are models that describe how an agent can take actions to transition between states, receiving rewards for its actions. Partially Observable Markov Decision Processes (POMDPs) are used to model MDPs where the true state is not known. Instead, the agent receives observations that are generated by the true state, and must infer what the true state is from the observations. Thus, the agent maintains a belief over true states which is updated as it receives new observations. In subsequent sections, we will refer to this belief over hidden states as $b$. The agent must then use this belief state to determine which action to take to maximize its expected value of the reward over time. This splits the POMDP into two main components, a state estimator and a policy generator. A typical graphical model for a POMDP is provided in figure~\ref{fig:pomdp}.

@@

\begin{figure}[H]
\begin{center}
	\begin{tikzpicture}[node distance = 1.7cm, auto]
		%actions
		\node [v] (ort) {$o_{t}$};
		\node [a, right of=ort] (oht) {$a_{t}$};
		\node [v, right of=oht] (ortp1) {$o_{t+1}$}; 
		\node [a, left of=ort] (ohtm1) {$a_{t-1}$};
		\node [v, left of=ohtm1] (ortm1) {$o_{t-1}$};
		% states
		\node [h, above of=ort] (st) {$s_t$}; 
		\node [h, above of=ortm1] (stm1) {$s_{t-1}$}; 
		\node [h, above of=ortp1] (stp1) {$s_{t+1}$}; 
		% edges; state -> obs
		\path [line] (st) edge (ort); 
		\path [line] (stm1) edge (ortm1); 
		\path [line] (stp1) edge (ortp1); 
		% state -> state
		\path [line] (stm1) edge (st); 
		\path [line] (st) edge (stp1); 
		% a -> state
		\path [line] (ohtm1) edge (st); 
		\path [line] (oht) edge (stp1); 
	\end{tikzpicture}
\caption{A graphical model representation of a POMDP}
\label{fig:pomdp}
\end{center}
\end{figure}

>>>>

\begin{abstract}
Robotic collaboration requires not just communication from the human to the robot, but also from the robot to the human. \stnote{Needs to get at the idea of speed and accuracy, that the robot needs to respond quickly, that the person is hard to understand.  Social feedback is our solution to a problem so you have to open with the problem.}   We call this robot-to-human communication \emph{social feedback}. In order to flexibly and intelligently generate social feedback, we present a partially Observable Markov Decision Process\stnote{name the model} that incorporates the human's belief about the robot's intent. Doing so incentivizes the robot to communicate its current state \stnote{using language and gesture} in order to allow the human participant to make informed decisions about their next actions. Initial evaluation in simulation shows \stnote{decreased interaction times} \stnote{cut: improvement in interaction length} in a simulated domain while maintaining near-perfect accuracy. 
\end{abstract}

@@

\stnote{cite}
Markov Decision Processes (MDPs) are models that describe how an agent can take actions to transition between states, receiving rewards for its actions. Partially Observable Markov Decision Processes (POMDPs) are used to model MDPs where the true state is not known. Instead, the agent receives observations that are generated by the true state, and must infer what the true state is from the observations. Thus, the agent maintains a belief over true states which is updated as it receives new observations. In subsequent sections, we will refer to this belief over hidden states as $b$. The agent must then use this belief state to determine which action to take to maximize its expected value of the reward over time. This splits the POMDP into two main components, a state estimator and a policy generator. A typical graphical model for a POMDP is provided in figure~\ref{fig:pomdp}.

@@

\begin{figure}[H]
\begin{center}
	\begin{tikzpicture}[node distance = 1.7cm, auto]
		%actions
		\node [v] (ort) {$o_{t}$};
		\node [a, right of=ort] (oht) {$a_{t}$};
		\node [v, right of=oht] (ortp1) {$o_{t+1}$}; 
		\node [a, left of=ort] (ohtm1) {$a_{t-1}$};
		\node [v, left of=ohtm1] (ortm1) {$o_{t-1}$};
		% states
		\node [h, above of=ort] (st) {$s_t$}; 
		\node [h, above of=ortm1] (stm1) {$s_{t-1}$}; 
		\node [h, above of=ortp1] (stp1) {$s_{t+1}$}; 
		% edges; state -> obs
		\path [line] (st) edge (ort); 
		\path [line] (stm1) edge (ortm1); 
		\path [line] (stp1) edge (ortp1); 
		% state -> state
		\path [line] (stm1) edge (st); 
		\path [line] (st) edge (stp1); 
		% a -> state
		\path [line] (ohtm1) edge (st); 
		\path [line] (oht) edge (stp1); 
	\end{tikzpicture}
\caption{A graphical model representation of a POMDP \stnote{cut}}
\label{fig:pomdp}
\end{center}
\end{figure}
